---
title: "Jan Wingate's Collections of Carex in Colorado"
author: "Rick Levy"
date: "Tuesday, April 17, 2018"
output: html_document
---
```{r setup, echo=FALSE}
options(warn=-1)
library(ggplot2)
```

```{r, results='hide', echo=FALSE}
jan_carex <- read.csv(file="jan_carex.csv")

#define window of map
long_colorado <- c(-125, -65)
lat_colorado <- c(20, 50)

```
---
This is a summary of Janet L. Wingates herbarium specimens of the genus Carex.

We analyzed all the records for the genus Carex colleccted by Janet L. Wingate found in
[SEINet](http://http://swbiodiversity.org).

There were a total of (N = `r nrow(jan_carex)`) specimens that were georeferenced.

```{r map, echo=FALSE}
world_map <- map_data("usa")

ggplot(jan_carex) + annotation_map(world_map, fill="gray40", colour="gray40") +
    geom_point(aes(x=decimalLongitude, y=decimalLatitude, color=specificEpithet),
               position=position_jitter(width=0.2, height=0.2)) +
    theme(panel.background = element_rect(fill="aliceblue"),
          legend.position = "none") +
    coord_map(projection = "mercator", orientation=c(90, 160, 0),
              xlim=long_colorado,  # limits on longitude
              ylim=lat_colorado) + # limits on latitude
   xlab("Longitude") + ylab("Latitude")


ggplot(jan_carex) +
  geom_bar(mapping = aes(x=scientificName)) +
  labs(x="Species",y="Number of Specimens",title="Numberof Specimens by Species")+
  theme (axis.text.x = element_text(size = 4, angle = 90,hjust = 1, vjust = 0))


